Digital History in Finland, 1488-1828

### 2016-06-23 inst/examples/manuscript-krakow.Rmd
Rmd update

  # Draw Figure
  theme_set(theme_bw(20))
  p <- ggplot(data = dfm, aes(x = date, y = Documents))
  p <- p + geom_line(col = "black")
  #p <- p + geom_smooth(col = "black")  
  p <- p + geom_point(col = "black", size = 3)
  p <- p + scale_x_continuous(breaks = seq(minyear, maxyear, 20), limits = c(minyear, maxyear))
  p <- p + ggtitle("Publishing activity")
  p <- p + ylab("Documents / Year")
  p <- p + xlab("Year")
  p = p + ylim(c(0, 80))
  p <- p + ggtitle(paste(myplace, " (", catal, ")", sep = ""))

>>>>

  # Draw Figure
  theme_set(theme_bw(20))
  p <- ggplot(data = dfm, aes(x = date, y = Documents))
  p <- p + geom_line(col = "black")
  #p <- p + geom_smooth(col = "black")  
  p <- p + geom_point(col = "black", size = 3)
  p <- p + scale_x_continuous(breaks = seq(minyear, maxyear, 20), limits = c(minyear, maxyear))
  p <- p + ggtitle("Publishing activity")
  p <- p + ylab("Documents / Year")
  p <- p + xlab("Year")
  p <- p + scale_y_continuous(limits = c(0, 100))  
  p <- p + ggtitle(paste(myplace, " (", catal, ")", sep = ""))
